Understanding the impacts of video-guided activities on parent-child interaction

### 2021-01-08 paper/manuscript.Rmd

The quantity and quality of early language input has been found to be strongly associated with later language and academic outcomes [@Hart1995; @Marchman2008; @Cartmill2013; @HirshPasek2015; see @Schwab2016 for a review]. Thus, because of the potential for large downstream effects [@Heckman2006], there is tremendous interest in interventions that change children's language environment. 
And because parents define a large portion of that environment, especially before the onset of formal schooling, parent behavior is a critical locus for such interventions. 
Many effective parenting interventions require large resource investments and require many hours of in-person contact [@Jamaica2014; @PerryPreschool2004; @Leung2018], making implementation at scale a daunting proposition. 
For this reason, many researchers targeting early language are interested in delivering parenting interventions remotely -- through texts, apps, and videos delivered on digital devices. 
But what do parents take away from these short messages about what to do with or how to talk with their children? 
In this paper, rather than conducting a large-scale intervention, we investigate the ways that parents change their local behavior with children immediately after seeing a short video instructing them on an activity, investigating one of the building blocks of many larger interventions.

>>>>

The quantity and quality of early language input has been found to be strongly associated with later language and academic outcomes [@Hart1995; @Marchman2008; @Rowe2012; @Cartmill2013; @HirshPasek2015; see @Schwab2016 for a review]. 
Thus, because of the potential for large downstream effects [@Heckman2006], there is tremendous interest in interventions that change children's language environment. 
And because parents define a large portion of that environment, especially before the onset of formal schooling, parent behavior is a critical locus for such interventions. 
Many effective parenting interventions require large resource investments and require many hours of in-person contact [@Jamaica2014; @PerryPreschool2004; @Leung2018], making implementation at scale a daunting proposition. 
For this reason, many researchers targeting early language are interested in delivering parenting interventions remotely -- through texts, apps, and videos delivered on digital devices. 
But what do parents take away from these short messages about what to do with or how to talk with their children? 
In this paper, rather than conducting a large-scale intervention, we investigate the ways that parents change their local behavior with children immediately after seeing a short video instructing them on an activity, investigating one of the building blocks of many larger interventions.
